---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shield

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of shield is to create a simple workflow to install package first level dependencies exclusively from github remote repositories when available.

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("yonicd/shield")
```
## Example

```{r}
library(shield)
library(details)
```

Map the dependencies to the github remote repositories and the current master sha

```{r}
desc_map <- create_map('DESCRIPTION')
```

```{r}
desc_map
```

Create a temp libpath to install to

```{r}
test_lib <- file.path(tempdir(),'mylib')
dir.create(test_lib)
```

Install the dependencies

```{r,eval = FALSE}
install_remotes(obj = desc_map,lib = test_lib)
```

<details><summary>Click To See Console Output</summary>

```{r, echo = FALSE}
install_remotes(obj = desc_map,lib = test_lib)
```

</details>

<br>

Install the package

```{r}
remotes::install_local(lib = test_lib,force = TRUE, upgrade = TRUE)
```

Check to see that everything was installed

```{r}
list.files(test_lib)
```

Check session_info of the default current libpath

```{details}
sessioninfo::package_info(list.files(test_lib))
```

Check session_info of the temp libpath

```{details}
withr::with_libpaths(test_lib,sessioninfo::package_info(list.files(test_lib)))
```
